Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-06-26 ms.qmd
Fix to fig in S

        annotate("text", x = 3.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$ =", p_value(round(pmcmc(t_VR_mean), digit = 2)))), hjust = 0, size = 8) + 
    annotate("text", x = 3.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
  annotate("text", x = 3.20, y = -2, label =paste0(round(mean(t_VR_mean_ef), 1), "%"), hjust = 0, size = 8) + labs(shape = "Type") + scale_fill_manual(values = c(col)) + annotate("text", y = 2.5, x = c(1.3, 2.3, 3.3)+0.1, label = TeX(paste0("\\it{k} = ", k_vr$k, " (", k_vr$sdy, ")")), size = 6)

>>>>

        annotate("text", x = 3.5, y = -2, label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ", " $\\,p_{MCMC}$ = ", p_value(round(pmcmc(t_VR_mean), digit = 2)))), hjust = 0, size = 8) + 
    annotate("text", x = 3.2, y = 1.5, label =TeX(paste0("$\\beta = $", "NS")), hjust = 0, size = 8) +
  annotate("text", x = 3.20, y = -2, label =paste0(round(mean(t_VR_mean_ef), 1), "%"), hjust = 0, size = 8) + labs(shape = "Type") + scale_fill_manual(values = c(col)) + annotate("text", y = 2.5, x = c(1.3, 2.3, 3.3)+0.1, label = TeX(paste0("\\it{k} = ", k_vr$k, " (", k_vr$sdy, ")")), size = 6)
